---
title: "Class 05"
output: html_document
date: "2026-09-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Game 01: subsetting Lists

```{r game01}
campus = jsonlite::fromJSON(
  "https://isa401-find-your-seat.vercel.app/campus.json")


names (campus) # shows the named elements within a list (or vector) or the
cols in a data frame
fsb = campus$Farmer
# saving the named farmer list in FSB
# equivalent I
fsb$code

## Reading the Excel
```{r occupations}
occupation = readxl::read_excel(
  path = "data/occupation.xlsx",
  sheet = 5, 
)
# - when you 
occupation = occupation [-c(32,33,34),]
```


## Reading the Excel
```{r occupations}
occupation = readxl::read_excel(
  path = "../data/occupation.xlsx",
  sheet = 5, 
)
# - when you 
occupation = occupation [-c(32,33,34),]
```

## Read JSON Files 
```json_url = paste0(
  "https://data.cincinnati-oh.gov/",
  "resource/rvmt-pkmq.json?$limit=100")
crashes_json = jsonlite::fromJSON(json_url)
dplyr::glimpse(
  crashes_json[, c("crashdate", "dayofweek",
                   "crashseverity", "age")])
```
## Class Game Two 

